---
title: "Predict Fertility using the swiss Data"
author: "DRManiar"
date: "10 October 2020"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction

- This `shiny` app is a simple demonstration of multivariate linear regression using `lm` function.
- The app uses `swiss` data.

```{r}
library(datasets)
data(swiss)
```

```{r echo=TRUE}
head(swiss)
```

## Output Template

```{r}
modFit <- lm(Fertility ~ Agriculture, data=swiss)
mse <- sqrt(sum(modFit$residual^2)/nrow(swiss))
xp <- 1:nrow(swiss)
plot(xp, swiss$Fertility,
     xlab = "Index",
     ylab = "Fertility",
     pch=1,
     col="blue")
points(xp,
       modFit$fitted.values,
       pch=19,
       col="red")
legend("topright",
       pch = c(1,19),
       col = c("blue", "red"),
       legend = c("Data", "Prediction"))
text(x=mean(c(max(xp),min(xp))),
     y=40,
     paste("MSRE = ", round(mse,2)))
summary(modFit)$coef
```


## Inputs & Outputs

There are two inputs desired from the user:

- Predictor variables, and
- X-axis Variable for plotting.

Based upon the user's input, the following output is displayed:

- A `scatter` plot showing:
  + Fertility data plotted against selected x-axis variable,
  + fitted.values plotted against selected x-axis variable, and
  + MSRE of the predictions.
- A table showing summary of linear fit model coefficients.

## How to Use the App

Follow the steps below:

- To generate a `new prediction`:
  + Select predictor variables using the check boxes,
  + Select the predictor for plotting, and
  + Hit **Submit** button to update the plot and summary table.
- To `reset` the app, click *"circular arrow"* towards the upper left corner of the app.
- To read this documentation, click on the `Documentation` tab.
- To view the predictions, click on the `Prediction` tab.
